Background Subtraction via Deep Variation Transformation

### 2018-07-03 draft.tex
增加图1，表达论文思想
none

%本文的想法和优势
The previous methods have already made great progress in generating some sophisticated background models with given videos. Unfortunately, some instructive clues have been long put aside and neglected, since there is no efficient way to deal with them. For instance, the static methods model the pixel-wise distribution of historical observations over time, while having no concerns over the sequential information in a video stream. To solve this problem, we bring up a novel conception of pixel variation transformation, wherein the historical observations of each pixel are conceived as a unity, the pixel variation. Each piece of pixel variation contains the complete temproal information of historical observations, which turns out to be our advantage that not only the distribution of observations, but also the temporal coherence plays an important role in the task.

@@

%文章结构
The outline of this paper is as follows: In Section II, we give a brief discussion about the early and recent relevant works. The details of the variation transformation are presented in Section III. The proposed fully convolutional network is illustrated in Section IV, followed by experiments and result comparison in Section V and conclude the paper in Section VI. 
\section{Related Work}
% XXX 引用文章的方式，Bouwmans2014 在ref.bib文件里,不懂去问曲师兄！！！！
\cite{Bouwmans2014}
Over the last few decades, Background subtraction has been well studied. Meanwhile, a huge number of methods were proposed. 
These methods can be broadly categorized into pixels-based, region-based and Deep Learning based methods.
\subsection{pixels-based methods}
The most widely used algorithms in Background subtraction are pixels-based methods. 
And one of the famous method is Gaussian Mixture Model (GMM), in which a GMM is used to model the history over time of pixel’s intensity values. 
It is assumed that pixels are independent from their neighbors. 
Incoming pixels are labeled as background if there exists a Gaussian in the GMM, where the distance between its mean and the pixel lies within a certain bound. 
For learning the parameters, that maximize the likelihood, the authors proposed an online method that approximates the Expectation Maximization (EM) algorithm.

In XXX , Mingliang Chen et al. 
propose a background subtraction algorithm using hierarchical superpixels segmentation, spanning trees and optical flow. 
Their Background model combine the GMM with constrains of temporal and spatial from optical flow and superpixels.

>>>>

%本文的想法和优势
The previous methods have already made great progress in generating some sophisticated background models with given videos. Unfortunately, some instructive clues have been long put aside and neglected, since there is no efficient way to deal with them. For instance, the statistical methods model the pixel-wise distribution of historical observations over time, while having no concerns over the sequential information in a video stream. To solve this problem, we bring up a novel conception of pixel variation transformation, wherein the historical observations of each pixel are conceived as a unity, the pixel variation. Each piece of pixel variation contains the complete temproal information of historical observations, which turns out to be our advantage that not only the distribution of observations, but also the temporal coherence plays an important role in the task.

@@

%文章结构
The outline of this paper is as follows: In Section II, we give a brief discussion about the early and recent relevant works. The details of the variation transformation are presented in Section III. The proposed fully convolutional network is illustrated in Section IV, followed by experiments and result comparison in Section V and conclude the paper in Section VI. 
\section{Related Work}
% XXX 引用文章的方式，Bouwmans2014 在ref.bib文件里,不懂去问曲师兄！！！！
\cite{Bouwmans2014}
Over the last few decades, background subtraction has been well studied. Meanwhile, a huge number of background modeling methods have been proposed. 
These methods can be broadly categorized into pixels-based, region-based and Deep Learning based methods.
\subsection{pixels-based methods}
Pixels-based methods are generally based on low-level features, such as color and gradients, these methods are computationally efficient and easy to deploy. However, they demonstrate a poor performance in modelling some challenging scenes, like illumination changing and intermittent object motion.
The most popular approaches are Gaussian Mixture Model (GMM) and its improved methods, which utilize a mixture of weighted Gaussians to model the probability distribution of each pixel over time. 
Mingliang Chen et al. proposed a Spatiotemporal GMM algorithm, which combines the GMM with constrains of temporal and spatial information from the optical flow and superpixels.

. 
Each pixels are assumed to be independent from their neighbors.

%
low-level features (e.g. color intensities, gradients pixel-based

PBAS [10] and ViBe+ [14], follow this paradigm as they are both based on stochastic intensity sampling.
Parametric approaches based on Gaussian Mixture Models (GMM) [15] or non-parametric ones based on Kernel Density Estimation (KDE)  
%
